---
title: "Practical Machine Learning Course Project"
author: "Zhang,Xiaoyu"
date: "Sunday, May 24, 2015"
output: html_document
---
# Introduction
## Background
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset). 

## Data Source
The training data for this project are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment. 

# Processing
## Load the data and required library
```{r}
require(caret)
require(randomForest)
training <- read.csv("./pml-training.csv", na.strings=c("NA","#DIV/0!", ""))
testing <- read.csv("./pml-testing.csv", na.strings=c("NA","#DIV/0!", ""))
```
## Cleaning the data
After thinking deep about the question and looking at the dataset, the columns which are irrelevent to the question itself or are comprised of very dirty data could be removed:

- With majority of missing value (above 95%)
- With user and time information ("user_name", "raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp","new_window","num_window")
- With useless index number
```{r}
set.seed(1234)
training <- training[,which(colSums(is.na(training)) <  nrow(training)*0.95)]
training <- subset(training,select = -(1:7))
```
Now we have 53 columns and 19622 observations in our training dataset.
## Feature Selection - Remove redundant features
The Caret R packages provides the findCorrelation function which will analyze a correlation matrix of the data's attributes report on attributes that can be removed.

Here I remove the attributes with an absolute correlation of 0.75 and higher to reduce the features
```{r}
correlationMatrix <- cor(training[,1:52])
highlyCorrelated <- findCorrelation(correlationMatrix,cutoff=0.75)

training <- training[,-highlyCorrelated]
```
Now we have 33 columns in total including the response.
## Patitioning the data
The training data set contains 33 variables and 19622 obs.
The testing data set contains 33 variables and 20 obs.
In order to perform cross-validation, the training data set is partionned into 2 sets: subTraining (60%) and subTest (40%).
This will be performed using random subsampling without replacement.
```{r}
inTrain <- createDataPartition(y=training$class,p=0.6,list=FALSE)
training.training <- training[inTrain,]
training.testing <- training[-inTrain,]
```
## Fitting Model with Random Forests
```{r,cache=TRUE}
control <- trainControl(method="cv",allowParallel=TRUE)
modFit <- train(classe ~. ,data=training.training,method="rf",trControl=control)
```
## Evluate on test data
```{r}
pred1 <- predict(modFit,training.testing)
confusionMatrix(pred1,training.testing$classe)
```
The accuracy of the model is 0.9911. Our Test data set comprises 20 cases. With an accuracy above 99% on our cross-validation data, we can expect that very few, or none, of the test samples will be missclassified.
# Predict on test data
```{r}
predictfinal <- predict(modFit, testing)
predictfinal
```
# Submission
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(predictfinal)
```
