---
title: "Motor Trend - Auto Transmission Analysis"
author: "Zhang,Xiaoyu"
date: "Saturday, April 25, 2015"
output: pdf_document
---
# Executive Summary
Motor Trend, a magazine about the automobile industry is interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:
- “Is an automatic or manual transmission better for MPG”
- "Quantify the MPG difference between automatic and manual transmissions"

## Data Descriptive
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).
- mpg : Miles/(US) gallon
- cyl : Number of cylinders
- disp : Displacement (cu.in.)
- hp : Gross horsepower
- drat : Rear axle ratio
- wt : Weight (lb/1000)
- qsec : 1/4 mile time
- vs : V/S
- am : Transmission (0 = automatic, 1 = manual)
- gear : Number of forward gears
- carb : Number of carburetors

# Main Analysis
## Exploratory Analysis
```{r}
data(mtcars)
summary(mtcars[,c("mpg","am")])
```
## Data Pre-processing
Transform the cylinder and transmission data to factors
```{r}
mtcars <- transform(mtcars,cyl = factor(cyl))
mtcars <- transform(mtcars,am = factor(am,labels = c("Automatic","Manual")))

```
## Hypothesis Test
Null: $\beta_{automotic} = \beta_{manual}$ 

When building linear model, coefficient $\beta_{am}$ for $X_{am}$ is interpreted as the difference in the mean whem comparing two groups.
```{r}
fit <- lm(mpg ~ am, data = mtcars)
summary(fit)
```

## Quantify the Difference
Build the full model including all variables and select the variables using backward selection to capture the most variability.
```{r}
fit2 <- lm(mpg ~ .,data = mtcars)
fit2.best <- step(fit2,trace = F,k=log(nrow(mtcars)))
fit2.best
```
# Result
- As we can see from above, the P-value for $\beta_{am}$ is 0.000285 which reject the null hypothesis, which means there is a great difference in different type of transmission
- The coefficient $\beta_{am}$ is positive which means Manual transmission is better for MPGX
- The MPG difference is $\beta_{am}$, which is 2.936

## Appendix
```{r,fig.height=3,fig.width= 4}
boxplot(mpg ~ am,data = mtcars)
```
```{r}
par(mfrow=c(2,2))
plot(fit2.best)
```
